How to compute the fusion product of MV cycles in type A

### 2021-03-01 draft.tex
some comments from anne and roger

Set $\cO = \CC\xt$ and $\cK = \CC\xT$. We will also need the notation $\cO_s = \CC\xt[t-s]$ for the completion of the local ring $\CC[t]$ at $s\in\spec\CC$ and $\cK_s$ for its fraction field $\CC\xT[t-s]$, as well as $\Kinf = \CC\xT[t^{-1}]$ \acom{for the fraction field of the completion of $\CC[t]$ at $\infty$?} 
\jcom{That wouldn't quite make sense.  Maybe this would be the place to define these disks $D_\infty$ and then we could say the function field of the disk.} 
% TODO: given by or described by?
% 
Note that (by changing the local coordinate on $\spec\CC[t]$ to $t-s$) we can identify $\cO_s \cong \cO$ and $\cK_s\cong\cK$.

@@

Set $\PP = \PP^1$. We will study formal spectra of $R$ and $K$ as formal disks in $\PP$. \acom{TODO: talk about discs.}

@@

Fix $G = \GL_m$ and let $T\subset G$ be the maximal torus of diagonal matrices. 
% are there other possibilities?? :S 
Write $P$ for the coweight lattice of $T$, so we have $P\cong \ZZ^m$.  The dominant coweights of $ G $ is the set of $ \lambda = (\lambda_1, \dots, \lambda_m) $ such that $ \lambda_1 \ge \cdots \ge \lambda_m$.  We also need the notion of effective dominant coweight, 
% \acom{can we conflate or should we be precise and say coweight?} \jcom{Corrected, let's stick to coweights.}
which means those $ \lambda $ as above with $ \lambda_m \ge 0$.  So an effective dominant coweight $ \lambda $ is a partition of $ \lambda_1 + \cdots + \lambda_m$, which we call the size of $ \lambda$. Write $P_+$ for dominant and $P_{++}$ for effective dominant.

@@

\subsection{Lattices}
\label{ss:lat}
We will use the lattice model, so it is useful to recall the following definition. Let $ R \subset K$ be two rings (usually, but not always, $K$ will be a field 
% \acom{When is $K$ not a field?}). Let $ m \in \mathbb N$ \acom{we have already fixed $m$?} and; e.g. K = C[t,t^{-1}] is not a field!!! 
Consider $ K^m $ as a $K$-module. By restriction $ K^m$ can be viewed as an $R$-module.  An $R$-lattice in $K^m$ 
% \acom{what is $M$? should be $K^m$?}; bc Joel was thinking about arbitrary free modules 
is an $R$-submodule $ L \subset K^m$ such that $ L $ is a free rank $ m $ $R$-module and $ L \otimes_R K = K^m $.  Equivalently, $ L = \Sp_R(v_1, \dots, v_m)$ where $v_1, \dots, v_m$ are free generators of $K^m$. \jcom{Maybe need that both $K$ and $R$ are integral domains and have the same field of fractions?} \acom{Roger proved it.}
% is this true?

% The trivial lattice is 
$L_0 = L_0(R) = R^m \subset K^m $ is called the standard lattice. The group $\GL_m(K) $ acts transitively on the set of $R$-lattices in $K^m$, thus giving a bijection between 
% the set of such lattices 
this set and $\GL_m(K)/\GL_m(R)$. \acom{Maybe abuse notation and warn the reader.}

We will be particularly interested in $\CC[t]$-lattices in $ \CC(t)^m$.  Given such a lattice $ L $ and a point $ a \in \CC$, the specialization of $ L $ at $ a $ is defined as
$$
% L(a) := L \otimes_{\CC[t]} \CC\xt[t-a] \subset \CC\xT[t-a]^m\,.
L(a) := L \otimes_{\CC[t]} \cO_a \subset \cK_a^m\,.
$$
We say that $ L $ is trivial at $ a $ if $ L(a) = \cO_a^m$. 
% \acom{Do we want to employ the notation $\cO_a$ and $\cK_a$ here?}
For example, the lattice $(t-s)^{-1}\CC[t] \subset \CC(t)$ is trivial at any $a\ne s$.

@@

\begin{itemize}
    \item The ordinary affine Grassmannian $\Gr = G(\cK)/G(\cO)$. It is described in modular terms by 
    $$
    \Gr = \{ (P, \varphi) : \text{$V$ is a rank $m$ vector bundle on $ D_0 $, $\varphi : V \xrightarrow{\sim} V_0 $ on $ D_0 \setminus \{0\} $} \} 
    $$
    where $V_0$ is the trivial rank $m$ vector bundle, and $ D_0$ is the formal disk centered at $ 0 \in \PP$.

    We also have a lattice description 
    $$ 
    \Gr = \{ L \subset \cK^m : \text{ $L$ is a $\cO$-lattice} \}\,.
    $$
    % 
    \item For any $ s \in \CC $, 
    % \acom{should it be $\AA$ instead of $\CC$} 
    the ordinary affine Grassmannian $\Gr_s = G(\cK_s)/G(\cO_s)$ at $ s $. It is described in modular terms by
    $$
    \Gr_s = \{ (P, \varphi) : \text{$V$ is a rank $m$ vector bundle on $ D_s $, $\varphi : V \xrightarrow{\sim} V_0 $ on $ D_s \setminus \{s\} $} \} 
    $$
    where $D_s$ is the formal disk centered at $s$ viewed as an element of $\PP$.

    We also have a lattice description 
    $$ 
    \Gr_s = \{ L \subset \cK_s^m : \text{ $L$ is a $\cO_s$-lattice} \} \,. 
    $$   
    \item The thick affine Grassmannian $\Grth = G(\Kinf)/G(\CC[t])$. % \CC\xT[t^{-1}]
    It is described in modular terms by
    $$
        \Grth = \{ (P, \varphi) : \text{$V$ is a rank $m$ vector bundle on $ \PP $, $\varphi : V \xrightarrow{\sim} V_0 $ on $ D_\infty $ } \} % (a disk centered at $ \infty$)
    $$
    where $D_\infty$ denotes a disk centered at $ \infty$. 
    % \acom{What is the difference between ``a disk'' and ``the formal disk''} \jcom{No difference.}

    We also have a lattice description 
    $$ 
    \Grth = \{ L \subset  \Kinf^m : \text{ $L$ is a $\CC[t]$-lattice} \}\,.
    $$ % \CC((t^{-1}))^m

@@

    Finally, it is given in lattice terms as the identity on the lattice and using the inclusion $\CC[t, t^{-1}, (t-s)^{-1}]^m \rightarrow \Kinf^m$ on the ambient spaces.
    \item The fibres $ \Gr_{0,s}$ of $ \Grbd \rightarrow \AA$ can be described as % are given as follows
    $$
    \Gr_{0,s} \cong 
    \begin{cases} 
        \Gr \times \Gr_s & s \ne 0 \\
        \Gr              & s = 0\,.
    \end{cases}
    $$
    In the $s\ne 0$ case, the isomorphism is given in the modular realization by restricting the vector bundle and trivializing to the appropriate disks.  
    In the lattice realization, it is given by forming tensor products 
    $$
    L \mapsto (L(0), L(s))\,.
    $$
    % in the $ s \ne 0 $ case.
    \jcom{Maybe we should introduce some notation for this isomorphism.}
    % \acom{Ok. Question: how is the isomorphism given at $s=0$?}
    \acom{Ok. TODO. Also write this in group theoretic terms. Probably $[g] \mapsto ([g],[g])$ is ok. Since $g\CC[t]\otimes_{\CC[t]}\cO_s \cong g\cO_s $ for some reason, where $g\in\CC[t,t^{-1},(t-s)^{-1}]$ can be viewed as $g\in\cK_s$.}

@@

    \item The locus $\cW_\mu = G_1\xt[t^{-1}]L_\mu \subset \Grth $.  
    \acom{want $t^\mu\CC[t]$ as opposed to $L_\mu$ here? Use thick $L_0$, $L_\mu$. $t\in R$, $t^\mu L_0(R)$. Or just use $t^\mu$.}
    In modular terms, this corresponds to the locus of those $ (V, \varphi)$ such that $ V $ is isomorphic to the trivial vector bundle on $ \PP$ and such that $ \varphi$ preserves the {Harder--Narasimhan filtration of $V$ at $ \infty$}.  The lattice description of $ \cW_\mu \cap \Grth^+$ is given in Lemma \ref{le:Wmu} below.

@@

    \item The ``upper-triangular'' MVy slice $\TT^{\mu_1, \mu_2,+}_\AA \rightarrow \AA $, defined by
    $$
    \TT^{\mu_1, \mu_2,+}_\AA := \{ (A,s) \in \TT_\mu \times \AA : g(A)_{ii} = t^{\mu_{1,i}} (t-s)^{\mu_{2,i}}, g(A)_{ij} = 0 \text{ for $ j < i $ }\}
    $$
    So a matrix in $\TT^{\mu_1, \mu_2,+}_\AA  $ is weakly block upper-triangular and its diagonal blocks are given by the companion matrices for the polynomials $t^{\mu_{1,i}} (t-s)^{\mu_{2,i}}$.

    Note that the fibre $  \TT^{\mu_1, \mu_2,+}_{0,0}$ is the same as the intersection of $ T^\mu $ with the strictly upper triangular matrices.

@@

\begin{lemma} \label{le:Grl1l2}
    Let $ L \in \Grth^+ $.  Let $ s \in \AA, s \ne 0 $.  The following are equivalent:
    \begin{enumerate}
        \item $ L $ is in the image of the map $ \Gr^{\lambda_1, \lambda_2}_s \rightarrow \Grth^+$
        \item The linear operator $ t $ on $ L_0/L$ has Jordan type $(0,\lambda_1), (s,\lambda_2)$.
        \item $ L \in G(\CC[t]) t^{\lambda_1} (t-s)^{\lambda_2}$ \acom{why no $G(\CC[t])$-coset?}
    \end{enumerate}
\end{lemma}

\begin{proof}
First we recall that for $ L \in \Gr^+$, $ L \in \Gr^{\lambda} = G(\CC[[t]])t^\lambda $ if and only if $ t |_{L_0/L} $ has Jordan type $ \lambda$.

    Now assume that $ L $ lies in the image of the map from $ \Gr^{\lambda_1, \lambda_2}_s$.  We know that $ L(0) \in \Gr^{\lambda_1}, L(s) \in \Gr^{\lambda_2} $.  This means that $t $ acting on $ \CC[[t]]^m / L(0)$ has Jordan type $ \lambda_1$ and $ t$ acting on $ \CC[[t-s]]^m / L(s) $ has Jordan type $ \lambda_2$.  Now, the map $ L_0 / L \rightarrow \CC[[t]]^m / L(0)$ induces an isomorphism between the $0$-generalized eigenspace of $ t$ and $ \CC[[t]]^m / L(0)$.    This shows that (i) implies (ii) and the logic can be reversed to see that (ii) implies (i).

    On the other hand, if $ L = g t^{\lambda_1} (t-s)^{\lambda_2} $ for some $ g \in G(\CC[t])$, then $ L(0) = g t^{\lambda_1} $ since $ (t-s)^{\lambda_2} \in G(\CC[[t]])$.  In this way, we see that (iii) implies (ii) and the logic can be reversed to get the equivalence.
\end{proof}

\begin{lemma} \label{le:Wmu}
    Let $ L \in \Grth^+$.  The following are equivalent:
    \begin{enumerate}
        \item $ L \in \cW_\mu$.
                \item $ L = Span_\cO(v_1, \dots, v_m)$ for some $ v_i $ of the form $ v_i = t^{\mu_i} e_i + \sum_{j=1} p_{ij} e_j $ where $ p_{ij} \in \CC[t] $ has degree less than $ \min(\mu_i, \mu_j)$.
        \item $ \beta_\mu := \{ [t^k e_i] : 0 \le k < \mu_i, 1 \le i \le m\}$ forms a basis for $ L_0/L$.

@@

\begin{proof}
    Let $ L \in \cW_\mu$.  Then $ L = Span_\cO(v_1, \dots, v_m) $ for some $ v_i $ with $ v_i = t^{\mu_i} e_i + \sum_{j=1} q_{ij}t^{\mu_i} e_j $ and $ q_{ij} \in t^{-1} \CC[[t^{-1}]]$.  Since $ L \in \Grth $, we see that $ v_i \in L_0$ which mean that $ p_{ij} := q_{ij}t^{\mu_i} \in \CC[t]$.  If $ \mu_j < \mu_i$, then we can alter this basis to $ v'_i = v_i - r v_j$ for some polynomial $r \in \CC[t]$ and thus ensure that $ p_{ij} $  has degree less than $ \min(\mu_i, \mu_j)$.  Thus (i) implies (ii).

    Suppose that $ L = Span_\cO(v_1, \dots, v_m)$ as in (ii).  Then $[t^{\mu_i} e_i] \in Span_\CC(\beta_\mu) $
in $ L_0/L$.  For this, we can deduce that $ \beta_\mu$ forms a basis for $ L_0/L$.  Hence (ii) implies (iii).  
    Finally, if we know that $ \beta_\mu $ forms a basis, then $ v_i := t^{\mu_i} e_i - \sum_{j=1} p_{ij} e_j \in L $ for some $ p_{ij} \in \CC[t]$ of degree less than $ \mu_j $.  It is easy to see that $ L = Span_\cO(v_1, \dots, v_m) $ and so $ L \in \cW_\mu$.  
    \end{proof}

@@

\begin{proof}
    Let $ L $ lie in this image.  Then $ L = g t^{\mu_1} (t-s)^{\mu_2}$ from some $ g \in N(\CC[t, t^{-1}, (t-s)^{-1}]) $.  Let $ h =(t-s)^{\mu_2} t^{-\mu_2}  $.  Note that $ h \in T_1\CC([[t^{-1}]])$. Then,
    $$ L = h (h^{-1} g h) t^{\mu}$$
    Note that $ h^{-1} g h \in N(\CC((t^{-1})))$ and from KWWY \jcom{Check this}, we know that $ (h^{-1} g h) t^{\mu} \in \cW_\mu$ and so the result follows.
    \end{proof}

@@

\begin{theorem} 
The map $ T_\mu \rightarrow \Grth^+ \cap \cW_\mu $ given by $ A \mapsto g(A) $ is an isomorphism with inverse given by
$$ L \mapsto [t|_{L_0/L} ]_{\beta_\mu}$$
\end{theorem}

\jcom{Do we have a reference?}
\acom{Your paper with Sabin??}
\jcom{I took at a look at Mirkovic-Vybornov (both versions) and at my paper with Sabin.  In Mirkovic-Vybornov, there is nothing about the image of the map.  In the paper with Sabin, we describe the image as $ L \subset L_0$, $[e_1], \dots $ forms a basis and $ z^{\mu_i} e_i \in W_{\mu_i} + L$.  I don't know why I put that third condition.  It seems automatic to me, since from the ``basis'' condition we know that $ W_{\mu_i} + L = L_0$.  Anyway, I think that I will try to write out the proof again for this paper.}

@@

In a similar way, we will write $ \overline{\OO}^{\lambda_1, \lambda_2}_\AA \cap T^\mu$, using the non-injective map $ \overline{\OO}^{\lambda_1, \lambda_2}_\AA \rightarrow M_N(\CC)$ (for example the fibre of this map over $ 0 $ is $ \CC $).

\begin{theorem} \label{th:OGrl}
    There is an isomorphism
    $$\overline{\OO}^{\lambda_1, \lambda_2}_\AA \cap T_\mu \cong \overline{Gr}^{\lambda_1, \lambda_2}_\AA \cap \cW_\mu $$
    given by $ (A,s) \mapsto (g(A), s)$.
\end{theorem}

\begin{theorem}
    The isomorphism from Theorem \ref{th:OGrl} restricts to an isomorphism
    $$ \overline{\OO}^{\lambda_1, \lambda_2}_\AA \cap T^{\mu_1, \mu_2, +}_\AA \cong \overline{Gr}^{\lambda_1, \lambda_2}_\AA \cap S^{\mu_1, \mu_2}_\AA$$
\end{theorem}

\jcom{I was thinking about the proof of this result.  It is enough to prove that for $ A \in \OO^{\lambda_1, \lambda_2}_s \cap \TT_\mu $, $g(A) \in S^{\mu_1, \mu_2}_s $ if and only if $ A \in T^+$.  It is easy to show that if $ A \in T^+$, then $ g(A) \in S^{\mu_1, \mu_2}_s $.  But the converse is not so obvious.  (I think Anne's paper/thesis might be incomplete on this point.)  I thought of two approaches: first to write down the lattice interpretation of $S^{\mu_1, \mu_2}$ (similar to what is in my thesis in the Anderson-Kogan comparison section) or think about both $S^{\mu_1, \mu_2}$ and $ T^+ $ as attracting sets for a $\CC^\times$ action.  Which do you prefer?}

\section{Falling Action} % Resolution

@@

    To see this, we use that $ L $ 
 has a $\CC[t]$-basis of the form 
    \begin{equation}
        v_i = t^{\mu_i} + \sum_{j>i} p_{ij}(t) e_j 
    \end{equation}
    with $\deg p_{ij}(t) < \mu_i = \mu_{1,i} + \mu_{2,i}$ ($1\le i\le m$).
    \acom{I don't know why this should be true. We might have to just define fibres of $\cW_{\mu_1,\mu_2}$ in this way?}
    \item $t\big|_{\CC[t]^m/L}$ will have two eigenvalues, 0 and $s$, and its generalized 0-eigenspace will have block type $\le \lambda_1$ while its generalized $s$-eigenspace will have block type $\le \lambda_2$. 
    To see this, note that there is a natural isomorphism
    $$\CC[[t]]^m/(L \otimes_{\CC[t]} \CC[[t]]) = \text{generalized $0$ eigenspace of $t$ on } \CC[t]^m/L$$
    carrying the action of $t $ to the action of $t$.

    The left hand side is the same thing as
    $$ \CC[[t]]^m / (L \otimes_{\CC[t]} \CC[[t]]) = (\CC[t]^m/L) \otimes_{\CC[t]} \CC[[t]] $$

>>>>

Set $\cO = \CC\xt$ and $\cK = \CC\xT$. We will also need the notation $\cO_s = \CC\xt[t-s]$ for the completion of the local ring $\CC[t]$ at $s\in\spec\CC$ and $\cK_s$ for its fraction field $\CC\xT[t-s]$, as well as $\Kinf = \CC\xT[t^{-1}]$.

% \acom{for the fraction field of the completion of $\CC[t]$ at $\infty$?} 
\jcom{That wouldn't quite make sense.  Maybe this would be the place to define these discs $D_\infty$ and then we could say the function field of the disc.} 
% TODO: given by or described by?
%

Note that (by changing the local coordinate on $\spec\CC[t]$ to $t-s$) we can identify $\cO_s \cong \cO$ and $\cK_s\cong\cK$.

@@

\acom{Set $\PP = \PP^1$. We will study formal spectra of $R$ and $K$ as formal discs in $\PP$.}
% \acom{TODO: talk about discs.}

@@

Fix $G = \GL_m$ and let $T\subset G$ be the maximal torus of diagonal matrices. 
% are there other possibilities?? :S 
Write $P$ for the coweight lattice of $T$, so we have $P\cong \ZZ^m$.  
\acom{This assumes $G$ is defined over $\CC$ right?} 
Under this isomorphism the dominant coweights of $ G $ 
% is
are identified with the set of $ \lambda = (\lambda_1, \dots, \lambda_m) $ such that $ \lambda_1 \ge \cdots \ge \lambda_m$. 
We also need the notion of effective dominant coweight, 
% \acom{can we conflate or should we be precise and say coweight?} \jcom{Corrected, let's stick to coweights.}
which means those $ \lambda $ as above with $ \lambda_m \ge 0$.  So an effective dominant coweight $ \lambda $ is a partition of $|\lambda| = \lambda_1 + \cdots + \lambda_m$, which we call the size of $ \lambda$. Write $P_+$ for dominant and $P_{++}$ for effective dominant.

@@

\subsection{Lattices}
\label{ss:lat}
We will use the lattice model, so it is useful to recall the following definition. Let $ R \subset K$ be two rings (usually, but not always, $K$ will be a field). 
% \acom{When is $K$ not a field?}). Let $ m \in \mathbb N$ \acom{we have already fixed $m$?} and; e.g. K = C[t,t^{-1}] is not a field!!! 
Consider $ K^m $ as a $K$-module. By restriction $ K^m$ can be viewed as an $R$-module.  An $R$-lattice in $K^m$ 
% \acom{what is $M$? should be $K^m$?}; bc Joel was thinking about arbitrary free modules 
is an $R$-submodule $ L \subset K^m$ such that $ L $ is a free rank $ m $ $R$-module and $ L \otimes_R K = K^m $.  Equivalently, $ L = \Sp_R(v_1, \dots, v_m)$ where $v_1, \dots, v_m$ are free generators of $K^m$.

\jcom{Maybe need that both $K$ and $R$ are integral domains and have the same field of fractions?} 
\acom{Roger has proved that what is written is ok.}
% is this true?

% The trivial lattice is 
$ L_0(R) = R^m \subset K^m $ is called the standard lattice. 
We will abuse notation and dentoe $L(R)$ simply $L_0$ in the hope that the ring $R$ will be understood from the context. 
The group $\GL_m(K) $ acts transitively on the set of $R$-lattices in $K^m$, thus giving a bijection between 
% the set of such lattices 
this set and $\GL_m(K)/\GL_m(R)$. 
% \acom{Maybe abuse notation and warn the reader.}
\acom{is it clear that $\GL(R^m) \le \GL(K^m)$ is normal?}

We will be particularly interested in $\CC[t]$-lattices in $ \CC(t)^m$.  Given such a lattice $ L $ and a point $ a \in \CC$, the specialization of $ L $ at $ a $ is defined as
$$
% L(a) := L \otimes_{\CC[t]} \CC\xt[t-a] \subset \CC\xT[t-a]^m\,.
L(a) := L \otimes_{\CC[t]} \cO_a \subset \cK_a^m\,.
$$
We say that $ L $ is trivial at $ a $ if $ L(a) = \cO_a^m$. 
% \acom{Do we want to employ the notation $\cO_a$ and $\cK_a$ here?}
For example, the lattice $(t-s)^{-1}\CC[t] \subset \CC(t)$ is trivial at any $a\ne s$. 
\acom{it is a little bit uneven to have notation for $\cO^m$ but not for $\cO_a^m$?}

@@

\begin{itemize}
    \item The ordinary affine Grassmannian $\Gr = G(\cK)/G(\cO)$. It is described in modular terms by 
    $$
    \Gr = \{ (P, \varphi) : \text{$V$ is a rank $m$ vector bundle on $ D_0 $, $\varphi : V \xrightarrow{\sim} V_0 $ on $ D_0 \setminus \{0\} $} \} 
    $$
    where $V_0$ is the trivial rank $m$ vector bundle, and $ D_0$ is the formal disc centered at $ 0 \in \PP$.

    We also have a lattice description 
    $$ 
    \Gr = \{ L \subset \cK^m : \text{ $L$ is a $\cO$-lattice} \}\,.
    $$
    % 
    \item For any $ s \in \CC $, 
    % \acom{should it be $\AA$ instead of $\CC$} 
    the ordinary affine Grassmannian $\Gr_s = G(\cK_s)/G(\cO_s)$ at $ s $. It is described in modular terms by
    $$
    \Gr_s = \{ (P, \varphi) : \text{$V$ is a rank $m$ vector bundle on $ D_s $, $\varphi : V \xrightarrow{\sim} V_0 $ on $ D_s \setminus \{s\} $} \} 
    $$
    where $D_s$ is the formal disc centered at $s$ viewed as an element of $\PP$.

    We also have a lattice description 
    $$ 
    \Gr_s = \{ L \subset \cK_s^m : \text{ $L$ is a $\cO_s$-lattice} \} \,. 
    $$   
    \item The thick affine Grassmannian $\Grth = G(\Kinf)/G(\CC[t])$. % \CC\xT[t^{-1}]
    It is described in modular terms by
    $$
        \Grth = \{ (P, \varphi) : \text{$V$ is a rank $m$ vector bundle on $ \PP $, $\varphi : V \xrightarrow{\sim} V_0 $ on $ D_\infty $ } \} % (a disc centered at $ \infty$)
    $$
    where $D_\infty$ denotes a disc centered at $ \infty$. 
    % \acom{What is the difference between ``a disc'' and ``the formal disc''} \jcom{No difference.}

    We also have a lattice description 
    $$ 
    \Grth = \{ L \subset  \Kinf^m : \text{ $L$ is a $\CC[t]$-lattice} \}\,.
    $$ % \CC\xT[t^{-1}]^m

@@

    Finally, it is given in lattice terms as the identity on the lattice and using the inclusion $\CC[t, t^{-1}, (t-s)^{-1}]^m \rightarrow \Kinf^m$ on the ambient spaces.
    \item The fibres $ \Gr_{0,s}$ of $ \Grbd \rightarrow \AA$ can be described as % are given as follows
    $$
    \Gr_{0,s} \cong 
    \begin{cases} 
        \Gr \times \Gr_s & s \ne 0 \\
        \Gr              & s = 0\,.
    \end{cases}
    $$
    In the $s\ne 0$ case, the isomorphism is given in the modular realization by restricting the vector bundle and trivializing to the appropriate discs.  
    In the lattice realization, it is given by forming tensor products 
    $$
    L \mapsto (L(0), L(s))\,.
    $$
    % in the $ s \ne 0 $ case.
    \jcom{Maybe we should introduce some notation for this isomorphism.}
    % \acom{Ok. Question: how is the isomorphism given at $s=0$?}
    \acom{Ok. TODO. Also write this in group theoretic terms. Probably $[g] \mapsto ([g],[g])$ is ok. Since $g\CC[t]\otimes_{\CC[t]}\cO_s \cong g\cO_s $ for some reason, where $g\in\CC[t,t^{-1},(t-s)^{-1}]$ can be viewed as $g\in\cK_s$.}

@@

    \item The locus $\cW_\mu = G_1\xt[t^{-1}]L_\mu \subset \Grth $.  
    \acom{want $\TT_\mu\CC[t]$ as opposed to $L_\mu$ here? Use thick $L_0$, $L_\mu$. $t\in R$, $\TT_\mu L_0(R)$. Or just use $\TT_\mu$.}
    In modular terms, this corresponds to the locus of those $ (V, \varphi)$ such that $ V $ is isomorphic to the trivial vector bundle on $ \PP$ and such that $ \varphi$ preserves the {Harder--Narasimhan filtration of $V$ at $ \infty$}.  The lattice description of $ \cW_\mu \cap \Grth^+$ is given in Lemma \ref{le:Wmu} below.

@@

    \item The ``upper-triangular'' MVy slice $\UU^{\mu_1, \mu_2}_\AA \rightarrow \AA $, defined by
    $$
    \UU^{\mu_1, \mu_2}_\AA := \{ (A,s) \in \TT_\mu \times \AA : g(A)_{ii} = t^{\mu_{1,i}} (t-s)^{\mu_{2,i}}, g(A)_{ij} = 0 \text{ for $ j < i $ }\}
    $$
    So a matrix in $\UU^{\mu_1, \mu_2}_\AA  $ is weakly block upper-triangular and its diagonal blocks are given by the companion matrices for the polynomials $t^{\mu_{1,i}} (t-s)^{\mu_{2,i}}$.

    Note that the fibre $  \UU^{\mu_1, \mu_2}_{0,0}$ is the same as the intersection of $ \TT_\mu $ with the strictly upper triangular matrices.

@@

\begin{lemma} \label{le:Grl1l2}
    Let $ L \in \Grth^+ $.  Let $ s \in \AA, s \ne 0 $.  The following are equivalent:
    \begin{enumerate}
        \item $ L $ is in the image of the map $ \Gr^{\lambda_1, \lambda_2}_s \rightarrow \Grth^+$
        \item The linear operator $ t $ on $ L_0/L$ has Jordan type $(0,\lambda_1), (s,\lambda_2)$.
        \item $ L \in G(\CC[t]) t^{\lambda_1} (t-s)^{\lambda_2}$ 
        % \acom{why no $G(\CC[t])$-coset?}
    \end{enumerate}
\end{lemma}

\begin{proof}
First we recall that for $ L \in \Gr^+$, $ L \in \Gr^{\lambda} = G(\CC\xt)t^\lambda $ if and only if $ t |_{L_0/L} $ has Jordan type $ \lambda$.

    Now assume that $ L $ lies in the image of the map from $ \Gr^{\lambda_1, \lambda_2}_s$.  We know that $ L(0) \in \Gr^{\lambda_1}, L(s) \in \Gr^{\lambda_2} $.  This means that $t $ acting on $ \CC\xt^m / L(0)$ has Jordan type $ \lambda_1$ and $ t$ acting on $ \CC\xt[t-s]^m / L(s) $ has Jordan type $ \lambda_2$.  Now, the map $ L_0 / L \rightarrow \CC\xt^m / L(0)$ induces an isomorphism between the $0$-generalized eigenspace of $ t$ and $ \CC\xt^m / L(0)$.    This shows that (i) implies (ii) and the logic can be reversed to see that (ii) implies (i).

    On the other hand, if $ L = g t^{\lambda_1} (t-s)^{\lambda_2} $ for some $ g \in G(\CC[t])$, then $ L(0) = g t^{\lambda_1} $ since $ (t-s)^{\lambda_2} \in G(\CC\xt)$.  In this way, we see that (iii) implies (ii) and the logic can be reversed to get the equivalence.
\end{proof}

\begin{lemma} \label{le:Wmu}
    Let $ L \in \Grth^+$.  The following are equivalent:
    \begin{enumerate}
        \item $ L \in \cW_\mu$.
                \item $ L = \Sp_\cO(v_1, \dots, v_m)$ for some $ v_i $ of the form $ v_i = t^{\mu_i} e_i + \sum_{j=1} p_{ij} e_j $ where $ p_{ij} \in \CC[t] $ has degree less than $ \min(\mu_i, \mu_j)$.
        \item $ \beta_\mu := \{ [t^k e_i] : 0 \le k < \mu_i, 1 \le i \le m\}$ forms a basis for $ L_0/L$.

@@

\begin{proof}
    Let $ L \in \cW_\mu$.  Then $ L = \Sp_\cO(v_1, \dots, v_m) $ for some $ v_i $ with $ v_i = t^{\mu_i} e_i + \sum_{j=1} q_{ij}t^{\mu_i} e_j $ and $ q_{ij} \in t^{-1} \CC\xt[t^{-1}]$.  Since $ L \in \Grth $, we see that $ v_i \in L_0$ which mean that $ p_{ij} := q_{ij}t^{\mu_i} \in \CC[t]$.  If $ \mu_j < \mu_i$, then we can alter this basis to $ v'_i = v_i - r v_j$ for some polynomial $r \in \CC[t]$ and thus ensure that $ p_{ij} $  has degree less than $ \min(\mu_i, \mu_j)$.  Thus (i) implies (ii).

    Suppose that $ L = \Sp_\cO(v_1, \dots, v_m)$ as in (ii).  Then $[t^{\mu_i} e_i] \in \Sp_\CC(\beta_\mu) $
in $ L_0/L$.  For this, we can deduce that $ \beta_\mu$ forms a basis for $ L_0/L$.  Hence (ii) implies (iii).  
    Finally, if we know that $ \beta_\mu $ forms a basis, then $ v_i := t^{\mu_i} e_i - \sum_{j=1} p_{ij} e_j \in L $ for some $ p_{ij} \in \CC[t]$ of degree less than $ \mu_j $.  It is easy to see that $ L = \Sp_\cO(v_1, \dots, v_m) $ and so $ L \in \cW_\mu$.  
    \end{proof}

@@

\begin{proof}
    Let $ L $ lie in this image.  Then $ L = g t^{\mu_1} (t-s)^{\mu_2}$ from some $ g \in N(\CC[t, t^{-1}, (t-s)^{-1}]) $.  Let $ h =(t-s)^{\mu_2} t^{-\mu_2}  $.  Note that $ h \in T_1\CC(\xt[t^{-1}])$. Then,
    $$ L = h (h^{-1} g h) t^{\mu}$$
    Note that $ h^{-1} g h \in N(\CC\xT[t^{-1}])$ and from KWWY \jcom{Check this}, we know that $ (h^{-1} g h) t^{\mu} \in \cW_\mu$ and so the result follows.
    \end{proof}

@@

\begin{theorem} 
The map $ \TT_\mu \rightarrow \Grth^+ \cap \cW_\mu $ given by $ A \mapsto g(A) $ is an isomorphism with inverse given by
$$ L \mapsto [t|_{L_0/L} ]_{\beta_\mu}$$
\end{theorem}

\jcom{Do we have a reference?}
\acom{Your paper with Sabin??}
\jcom{I took at a look at Mirkovic-Vybornov (both versions) and at my paper with Sabin.  In Mirkovic-Vybornov, there is nothing about the image of the map.  In the paper with Sabin, we describe the image as $ L \subset L_0$, $[e_1], \dots $ forms a basis and $ z^{\mu_i} e_i \in W_{\mu_i} + L$.  I don't know why I put that third condition.  It seems automatic to me, since from the ``basis'' condition we know that $W_{\mu_i} + L = L_0$.  Anyway, I think that I will try to write out the proof again for this paper.}
\acom{Rather $(\sum W_{\mu_i} )+ L = L_0$? But yes we agree that the basis assumption is enough. Can try to prove by induction?}

@@

In a similar way, we will write $ \overline{\OO}^{\lambda_1, \lambda_2}_\AA \cap \TT_\mu$, using the non-injective map $ \overline{\OO}^{\lambda_1, \lambda_2}_\AA \rightarrow M_N(\CC)$ (for example the fibre of this map over $ 0 $ is $ \CC $).

\begin{theorem} \label{th:OGrl}
    There is an isomorphism
    $$\overline{\OO}^{\lambda_1, \lambda_2}_\AA \cap T_\mu \cong \Gr^{\lambda_1, \lambda_2}_\AA \cap \cW_\mu $$
    given by $ (A,s) \mapsto (g(A), s)$.
\end{theorem}

\begin{theorem}
    The isomorphism from Theorem \ref{th:OGrl} restricts to an isomorphism
    $$ \overline{\OO}^{\lambda_1, \lambda_2}_\AA \cap \UU^{\mu_1, \mu_2}_\AA \cong \overline{\Gr}^{\lambda_1, \lambda_2}_\AA \cap S^{\mu_1, \mu_2}_\AA$$
\end{theorem}

\jcom{I was thinking about the proof of this result.  It is enough to prove that for $ A \in \OO^{\lambda_1, \lambda_2}_s \cap \TT_\mu $, $g(A) \in S^{\mu_1, \mu_2}_s $ if and only if $ A \in T^+$.  It is easy to show that if $ A \in \UU$, then $ g(A) \in S^{\mu_1, \mu_2}_s $.  But the converse is not so obvious.  (I think Anne's paper/thesis might be incomplete on this point.)  I thought of two approaches: first to write down the lattice interpretation of $S^{\mu_1, \mu_2}$ (similar to what is in my thesis in the Anderson-Kogan comparison section) or think about both $S^{\mu_1, \mu_2}$ and $\UU$ as attracting sets for a $\CC^\times$ action.  Which do you prefer?}
% 
\acom{Assuming Theorem 2 we think this follows by application of Roger's lemma. Also, I think my thesis is complete on this point.}
% 
\section{Falling Action} % Resolution

@@

    To see this, we use that $ L $ 
 has a $\CC[t]$-basis of the form 
    \begin{equation}
        v_i = t^{\mu_i} + \sum_{j>i} p_{ij}(t) e_j 
    \end{equation}
    with $\deg p_{ij}(t) < \mu_i = \mu_{1,i} + \mu_{2,i}$ ($1\le i\le m$).
    \acom{I don't know why this should be true. We might have to just define fibres of $\cW_{\mu_1,\mu_2}$ in this way?}
    \item $t\big|_{\CC[t]^m/L}$ will have two eigenvalues, 0 and $s$, and its generalized 0-eigenspace will have block type $\le \lambda_1$ while its generalized $s$-eigenspace will have block type $\le \lambda_2$. 
    To see this, note that there is a natural isomorphism
    $$\CC\xt^m/(L \otimes_{\CC[t]} \CC\xt) = \text{generalized $0$ eigenspace of $t$ on } \CC[t]^m/L$$
    carrying the action of $t $ to the action of $t$.

    The left hand side is the same thing as
    $$ \CC\xt^m / (L \otimes_{\CC[t]} \CC\xt) = (\CC[t]^m/L) \otimes_{\CC[t]} \CC\xt $$
